---
title: "Who Represents You?"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
input_address = "4616 22nd Ave NE, seattle"
input_state = "WA"
```

##Your Representatives

This is a report about the political representatives based on the address in *Seattle, WA*. This report draws upon data from the [ProPublica API](https://projects.propublica.org/api-docs/congress-api/) and the [Google Civic Data API](https://developers.google.com/civic-information/). As an overview, here is a summary of who represents the address given (from the local to the national level).

```{r, message=FALSE, echo=FALSE, warning=FALSE}
source("civic-info.R")
kable(civic(input_address))
```

## House of Representatives

Now let's take a look at **all** of the congressional representatives (in the **House of Representatives**, *not* the Senate) for *Washington* state where the address was given. We see this breakdown by gender and political party for those members of the House:

```{r,message=FALSE, echo=FALSE, fig.width=8, fig.height=6}
source("propublica.R")
gender_plot
party_plot
```

## `r representative_name`

Here is one representative of current state, *`r representative_name`*. The representative is `r age` years old, learn more about this representative on twitter at [`r twitter`](`r twitter_site`). According to the data, in the most recent 20 congressional votes, the representative was in accordance with the majority `r agree_percent` of the time.


