---
title: "A7 Collaboration"
author: "ZeXin Lv, RuiJun Guo, YuTian Lei, Haowen Bao"
date: "2019/2/24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("scripts/function.R")
source("scripts/chart_1.R")
source("scripts/chart_2.R")
```

```{r ,include=FALSE}
data <- read.csv("data/wdvp.csv",  stringsAsFactors = F)
intro <- intro_function(data)
chart_1 <- chart_1(data)
chart_2 <- chart_2(data)
```

## Overview

This is a brief report using dataset from from World Data Visualization competition([source](https://wdvp.worldgovernmentsummit.org)). 
The data reveals that the country with the higest GDP per capita is `r intro$gdp_top$country_name`, with the GDP per capita `r intro$gdp_top$gdp_per_capita_ppp`. And the country with the highest gini index is `r intro$gini_index_top$country_name`, with the gini index `r intro$gini_index_top$gini_index`. The country with the highest happiness report score is `r intro$happiness_report_score_top$country_name`, with the score `r intro$happiness_report_score_top$world_happiness_report_score`.

## Chart 1

To find the relationship between GDP per capita and world happiness report score, here is a chart of of world data visualization competition:
`r chart_1`

## Chart 2

To find the relationship between world happiness report score and unemployment percentage, here is a chart of of world data visualization competition:
`r chart_2`
